%-------------------------
% Resume in LaTeX
% Based on Jake's Resume template
% License: MIT
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\usepackage[T1]{fontenc}

%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\setlength{\footskip}{4.1pt}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure PDF is machine readable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{#1 \vspace{-2pt}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Sheikh Suhail Khursheed} \\ \vspace{1pt}
    \small +91-7006386057 $|$
    \href{mailto:sheikhsuhailofficial@gmail.com}{\underline{sheikhsuhailofficial@gmail.com}} $|$
    \href{https://linkedin.com/in/sheikh-suhail-khursheed-280466190}{\underline{LinkedIn}} $|$
    \href{https://github.com/sheikhsuhail19}{\underline{GitHub}} $|$
    \href{https://leetcode.com/sheikhsuhail2026/}{\underline{LeetCode}}
\end{center}

%-----------SUMMARY-----------
\section{Summary}
  \small{Software Engineer with 3 years of experience building and optimizing high-throughput, distributed payment systems in the BFSI domain. Contributed to architectural decisions around cloud-native modernization, messaging design, and performance engineering for SEPA/Instant Payment platforms --- achieving a 5x throughput improvement. Contributes to system design discussions, mentors peers, and drives AI governance initiatives.}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Software Development Engineer - 2}{August 2023 -- Present}
      {SBS (formerly Sopra Banking Software)}{Noida, India}
    \resumeItemListStart
      \resumeItem{Drove performance engineering end-to-end: achieved 5x throughput improvement on the Instant Payment platform through Java code optimizations, JVM profiling, application and infra tuning, and load/burst/endurance testing --- establishing benchmarking practices adopted across teams.}
      \resumeItem{Strong functional knowledge of EU payment schemes --- SEPA Credit Transfer (SCT) and SEPA Instant (SCT Inst) including ISO 20022 messaging (pacs/pain), R-transactions, settlement cycles, and CSM integrations with STET, SWIFT (RT1, TIPS), Equens Worldline, and Faster Payments.}
      \resumeItem{Owned CI/CD pipeline design and containerization for services within a distributed monolith to cloud-native migration using Docker, Open Liberty, Helm, and Kubernetes --- modularized 15+ services with GitLab CI/CD.}
      \resumeItem{Strengthened system resilience --- implemented graceful startup/shutdown, circuit breakers for downstream dependency failures, dead-letter queues with idempotent retry strategies, ensuring zero message loss and fault tolerance.}
      \resumeItem{Identified and resolved a critical memory leak in a payment gateway connector via JVM profiling and memory analysis, stabilizing production under sustained load.}
      \resumeItem{Integrated Kafka for new microservices while ensuring backward compatibility with ActiveMQ/IBMMQ for legacy services --- enabling independent scaling and decoupled processing.}
      \resumeItem{Built observability dashboards, SLA monitoring, and alerting on Dynatrace --- enabling proactive incident detection and reducing MTTR during production operations.}
      \resumeItem{Led the transition from legacy SOAP services to RESTful APIs and replaced Hazelcast with Redis, reducing latency and improving cloud-native interoperability.}
      \resumeItem{Developed batch processing jobs for routing and reconciliation file ingestion from multiple CSMs.}
      \resumeItem{Part of AI Governance Squad --- contributed to GenAI developer guidelines, responsible adoption policies, and usage guardrails for the engineering organization.}
      \resumeItem{Part of the SaaS Ops team --- owned resilience, performance, and testing frameworks while managing customer onboarding, UAT coordination, go-lives across EU markets with zero downtime, and automated health-checks.}
      \resumeItem{Championed code review practices --- 60\% drop in post-release defects over 6 months; improved test coverage (backend 27\%\textrightarrow 60\%, frontend\textrightarrow 95\%).}
      \resumeItem{Spearheaded front-end migration from JSF to Angular 16+, improving page load times and UI responsiveness.}
      \resumeItem{Delivered technical workshops on Kafka, Redis, and JVM internals --- mentoring 4+ engineers and accelerating team onboarding to cloud-native patterns.}
    \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, TypeScript, Python, SQL, Bash, HTML/CSS} \\
     \textbf{Frameworks}{: Jakarta EE, MicroProfile, JBoss, Open Liberty, Spring Boot, Spring Batch, Hibernate, Angular 16+, Node.js, OAuth2} \\
     \textbf{Infra}{: Docker, Kubernetes, Helm, Kafka, Redis, ActiveMQ, IBMMQ, PostgreSQL, MySQL, AWS S3, Dynatrace, GitLab CI/CD, Linux} \\
     \textbf{Tools}{: YourKit, k6, JUnit, Mockito, Karma, Jasmine, SoapUI, Postman, SonarQube, Liquibase, Maven, Git, Jira, Confluence} \\
     \textbf{Practices}{: Distributed Systems, High Availability, Microservices, Event-Driven Architecture, REST API Design, ISO 20022, OOP, TDD, Design Patterns, JVM Internals, Performance Engineering, Agile/Scrum}
    }}
 \end{itemize}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Noida Institute of Engineering \& Technology}{Greater Noida, U.P.}
      {B.Tech in Computer Science \& Engineering --- CGPA: 8.78/10}{Jun 2019 -- Jun 2023}
  \resumeSubHeadingListEnd

%-----------ACHIEVEMENTS-----------
\section{Achievements}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     {Highest number of awards in the organization --- CI/CD improvements, production hotfixes, customer go-lives, Angular adoption, code reviews and code refactoring.} \\
     {Runner-up (Top 2/47 teams) in SBS Cybersecurity Hackathon.} \\
     {500+ DSA problems solved $|$ GATE 2023 qualified $|$ Fully funded scholarship for Bachelors degree.}
    }}
 \end{itemize}

%-------------------------------------------
\end{document}
